---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Diagnose Bioconductor package build failures

<!-- badges: start -->
[![R-CMD-check](https://github.com/csoneson/BiocBuildFailureDiagnosis/workflows/R-CMD-check/badge.svg)](https://github.com/csoneson/BiocBuildFailureDiagnosis/actions)
<!-- badges: end -->


The purpose of this repository is to collect functionality for diagnosing build failures in Bioconductor packages. Contributions from the community are welcome - please fork this repository and make a pull request with your contributions. Also add your name among the contributors below. 

For more information, refer to the corresponding entry in the [BiocChallenges](https://github.com/kevinrue/BiocChallenges/) repository. 

## Contributors

- Charlotte Soneson (@csoneson)
- Lluís Revilla Sancho (@llrs)

## Installation

You can install the released version of BiocBuildFailureDiagnosis from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("csoneson/BiocBuildFailureDiagnosis")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(BiocBuildFailureDiagnosis)
explainBiocBuildFailure("Rhisat2")
```
